Windowed Developer Topic Analysis

### 2009-04-01 lda-paper.tex
SOme conclusions

@@

>>>>

Our contributions include:
\begin{itemize}
\item Demonstrating the value of windowed topic analysis
\item Multiple visualizations of trends over time
\end{itemize}

@@

Even with our liberal topic similarity metrics which produced both
long and short and trends we showed that there are only a few trends
in a repository which re-appear. Since so few trends re-appear and so
many trends appear only once this suggests that global topic analysis
might be ignoring local unique topics.
